Oral anticoagulants

### 2020-12-16 r_notebooks/exploring_oral_anticoagulants_war_prop.Rmd
added propRegional to anticogulants as prop of warfarin

@@

```{r prep-data}
  propRegional <- function(data, region, datename = datename, unit = Quantity){
  # Function to create tsibble object for a proportion of a drug by a given `unit` 
  # per `datename`
  # e.g. countRegional(oc, Locality, datename, Quantity) is the `Quantity`
  # per `datename` grouped by `Locality` from `oc`. `Quantity` is corrected for
  # the number of days in each month.
  region <- enquo(region)
  datename <- enquo(datename)
  unit <- enquo(unit)

  data %>%
    mutate(regional_unit = as_factor(set_names(!!region))) %>%
    group_by(regional_unit, !!datename) %>%
    summarise(n = sum(!!unit)) %>%
    mutate(n = case_when(str_detect(!!datename, pattern = "-01-") ~ n/31,
                         str_detect(!!datename, pattern = "-02-") ~ n/28.25,
                         str_detect(!!datename, pattern = "-03-") ~ n/31,
                         str_detect(!!datename, pattern = "-04-") ~ n/30,
                         str_detect(!!datename, pattern = "-05-") ~ n/31,
                         str_detect(!!datename, pattern = "-06-") ~ n/30,
                         str_detect(!!datename, pattern = "-07-") ~ n/31,
                         str_detect(!!datename, pattern = "-08-") ~ n/31,
                         str_detect(!!datename, pattern = "-09-") ~ n/30,
                         str_detect(!!datename, pattern = "-10-") ~ n/31,
                         str_detect(!!datename, pattern = "-11-") ~ n/30,
                         str_detect(!!datename, pattern = "-12-") ~ n/31)) %>%
    ungroup() %>%
    as_tsibble(index = !!datename, key = regional_unit)
}

oac_monthly_quantity_hb <- 
  right_join(oac, select(gp, c(practiceid, hboard)), 
             by = c("PracticeID" = "practiceid")) %>%
  countRegional(hboard, datename, Quantity) %>% 
  left_join(gp %>% 
  select(c(practiceid, npat, hboard)) %>% 
  group_by(hboard) %>% 
  summarise(npat = sum(npat)), by = c("regional_unit" = "hboard")) %>% 
  mutate(n = 1000*n/npat) # quantity per 1000 pts

oac_monthly_quantity_cluster <- 
  right_join(oac, select(gp, c(practiceid, cluster)), 
             by = c("PracticeID" = "practiceid")) %>%
  countRegional(cluster, datename, Quantity) %>% 
  left_join(gp %>% 
  select(c(practiceid, npat, cluster)) %>% 
  group_by(cluster) %>% 
  summarise(npat = sum(npat)), by = c("regional_unit" = "cluster")) %>% 
  mutate(n = 1000*n/npat) # quantity per 1000 pts

oac_monthly_quantity_gp <- 
  countRegional(oac, PracticeID, datename, Quantity) %>% 
  right_join(select(gp, c(practiceid, npat)), 
            by = c("regional_unit" = "practiceid")) %>% 
  mutate(n = 1000*n/npat)

>>>>

## Function

propRegional <- function(data, region, datename = datename, unit = Quantity, 
                         bnf){
  # Function to create tsibble object for a proportion of a drug by a given `unit` 
  # per `datename`
  # e.g. propRegional(oc, Locality, datename, Quantity) is the `Quantity`
  # per `datename` grouped by `Locality` from `oc`. `Quantity` is corrected for
  # the number of days in each month.
  region <- enquo(region)
  datename <- enquo(datename)
  unit <- enquo(unit)

  data %>%
    mutate(regional_unit = as_factor(set_names(!!region))) %>%
    group_by(!!datename, bnfchem, regional_unit) %>% 
    summarise(n = sum(!!unit)) %>% 
    mutate(n = n / sum(n)) %>% 
    filter(bnfchem == bnf) %>% 
    mutate(n = case_when(str_detect(!!datename, pattern = "-01-") ~ n/31,
                         str_detect(!!datename, pattern = "-02-") ~ n/28.25,
                         str_detect(!!datename, pattern = "-03-") ~ n/31,
                         str_detect(!!datename, pattern = "-04-") ~ n/30,
                         str_detect(!!datename, pattern = "-05-") ~ n/31,
                         str_detect(!!datename, pattern = "-06-") ~ n/30,
                         str_detect(!!datename, pattern = "-07-") ~ n/31,
                         str_detect(!!datename, pattern = "-08-") ~ n/31,
                         str_detect(!!datename, pattern = "-09-") ~ n/30,
                         str_detect(!!datename, pattern = "-10-") ~ n/31,
                         str_detect(!!datename, pattern = "-11-") ~ n/30,
                         str_detect(!!datename, pattern = "-12-") ~ n/31)) %>%
    ungroup() %>%
    as_tsibble(index = !!datename, key = regional_unit)
}

@@

```{r prep-data}

oac_monthly_quantity_hb <- 
  right_join(oac, select(gp, c(practiceid, hboard)), 
             by = c("PracticeID" = "practiceid")) %>%
  propRegional(region = hboard, datename = datename, unit = Quantity,
               bnf = warf) %>% 
  left_join(gp %>% 
  select(c(practiceid, npat, hboard)) %>% 
  group_by(hboard) %>% 
  summarise(npat = sum(npat)), by = c("regional_unit" = "hboard")) %>% 
  mutate(n = 1000*n/npat) # quantity per 1000 pts

oac_monthly_quantity_cluster <- 
  right_join(oac, select(gp, c(practiceid, cluster)), 
             by = c("PracticeID" = "practiceid")) %>%
  propRegional(cluster, datename, Quantity) %>% 
  left_join(gp %>% 
  select(c(practiceid, npat, cluster)) %>% 
  group_by(cluster) %>% 
  summarise(npat = sum(npat)), by = c("regional_unit" = "cluster")) %>% 
  mutate(n = 1000*n/npat) # quantity per 1000 pts

oac_monthly_quantity_gp <- 
  propRegional(oac, PracticeID, datename, Quantity) %>% 
  right_join(select(gp, c(practiceid, npat)), 
            by = c("regional_unit" = "practiceid")) %>% 
  mutate(n = 1000*n/npat)
